My title

### 2022-03-22 outputs/paper/paper.Rmd
Minor Change

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Lantao Cui
  - Huakun Shen
  - Sijian Wu
thanks: "Code and data are available at: https://github.com/HuakunShen/Discrimination-Analysis-Canadian-2014-GSS"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "We studied discrimination in Canada and its related effects. Discrimination could potentially to inequality and even crimes. We found that sex discrimination is most common, the most common place for discrimination to happen is bank, store and retaurant; there is no apparent gender discrimination in law enforcement; and robbery is correlated with discrimination."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)

@@

Discrimination had always been a worldwide issue, in the past, people used to judge people based on their race, sex, and age. However, after going into the 20th century, people started to advocate for equality and diversity, along with the help of some civil rights leaders such as Martin Luther King, the world is slowly becoming more diversified and discrimination-free. But despite the efforts people make to promote equality, discrimination and inequality are still prominent in today’s world. For instance, according to Statistics Canada, in 2017, the number of hate crimes increased markedly by 47% and has remained at comparable levels in 2018 and 2019. Between 2018 and 2019, hate crimes motivated by hatred of a race or ethnicity increased by 10%, much of this increase was a result of more hate crimes targeting the Black and West Asian People. [@moreau_2021]

To find out more about discrimination, we obtained and analyzed data from Canadian General Social Survey, we are mostly interested in the type of discrimination that occurs most frequently and whether discrimination affects law enforcement. Additionally, we want to find out whether there is a correlation between discrimination and different type of crimes.

@@

```{r, include= FALSE}
myvars <- c("sex", "cip_10")
cip_based_on_gender <- input_csv[myvars]
# Only interested in valid responses
cip_based_on_gender<-cip_based_on_gender[!cip_based_on_gender$cip_10>=6,]
# Rename column
cip_based_on_gender$sex[cip_based_on_gender$sex==2] <- "Female"
cip_based_on_gender$sex[cip_based_on_gender$sex==1] <- "Male"
cip_based_on_gender$cip_10[cip_based_on_gender$cip_10==1] <- "Great confidence"
cip_based_on_gender$cip_10[cip_based_on_gender$cip_10==2] <- "Some confidence"
cip_based_on_gender$cip_10[cip_based_on_gender$cip_10==3] <- "Small confidence"
cip_based_on_gender$cip_10[cip_based_on_gender$cip_10==4] <- "No confidence"
# Generate table for plotting
cip_count_based_on_gender <- table(cip_based_on_gender$sex, cip_based_on_gender$cip_10)

@@

```{r, include = FALSE}
myvars <- c("sex", "plp_130", "plp_140")
pip_based_on_gender <- input_csv[myvars]
# Filter out valid response
pip_based_on_gender<-pip_based_on_gender[!(pip_based_on_gender$plp_130>=6 | pip_based_on_gender$plp_140>=6),]
# Rename column
pip_based_on_gender$sex[pip_based_on_gender$sex==2] <- "Female"
pip_based_on_gender$sex[pip_based_on_gender$sex==1] <- "Male"
pip_based_on_gender$plp_130[pip_based_on_gender$plp_130==1] <- "Good Job"
pip_based_on_gender$plp_130[pip_based_on_gender$plp_130==2] <- "Average Job"
pip_based_on_gender$plp_130[pip_based_on_gender$plp_130==3] <- "Poor Job"

@@

```{r, include = FALSE}
myvars <- c("sex", "pcc_145")
conf_in_court_based_on_gender <- input_csv[myvars]
# Filter out valid response
conf_in_court_based_on_gender<-conf_in_court_based_on_gender[!(conf_in_court_based_on_gender$pcc_145>=6),]
conf_in_court_based_on_gender$sex[conf_in_court_based_on_gender$sex==2] <- "Female"
conf_in_court_based_on_gender$sex[conf_in_court_based_on_gender$sex==1] <- "Male"
conf_in_court_based_on_gender$pcc_145[conf_in_court_based_on_gender$pcc_145==1] <- "Great Confidence"
conf_in_court_based_on_gender$pcc_145[conf_in_court_based_on_gender$pcc_145==2] <- "Some Confidence"
conf_in_court_based_on_gender$pcc_145[conf_in_court_based_on_gender$pcc_145==3] <- "Not Very Much Confidence"
conf_in_court_based_on_gender$pcc_145[conf_in_court_based_on_gender$pcc_145==4] <- "No Confidence"
# Generate table
conf_in_court_based_on_gender <- table(conf_in_court_based_on_gender$sex, conf_in_court_based_on_gender$pcc_145)

@@

## Limitations

There are some limitations in the data source which could cause inaccuracy.

In Figure \@ref(fig:crime-plot), we can see that the number of "theft of personal property" is over 1200. But in Figure \@ref(fig:crime-count-plot-by-education), the total number of "theft of personal property" is below 300, which is a fraction of the total number.
What happens to the rest of the population? Are their education level all below Elementary school? This is not very likely in Canada (a developer country). After carefully inspecting the data, I found that 88.6% of the samples didn't select a "Yes" or "No" answer for either of the 3 listed education levels. Most of the answers were "Valid Skip", causing the sample size to be quite small for education-related data.

Samples used to generate Figure \@ref(fig:crime-count-plot-by-education) is not the same group of sample (or just a small subset of the original sample) used to generate \@ref(fig:crime-plot). Further due to the smaller sample size, the conclusion drawn from the data could be very inaccurate.

For example, in Figure \@ref(fig:university-education-vs-crime), we can see that "Attempted theft of household property" is 100% for university-level-education population. We may come to a conclusion that people with higher education level are more likely to get stolen.

But 100% is not a regular number, it's not normal to reach 100% in large-sample survey, after carefully inspecting the dataset, only there is only one sample fall in the group "Attempted theft of household property" + "University Level Education", and none fall in the group "Attempted theft of household property" and "No University Level Education". This could be normal because it's possible that not many people experienced "Attempted theft of household property". But after further inspection I found that there are 20 samples selecting "Attempted theft of household property" and 19 of them has "Valid Skip" for education level survey. In brief, only 5% of the "Attempted theft of household property" samples are valid, and the sample size is 1. Without careful inspection to every piece of data, these invalid responses could lead to misinterpretation.

A large-enough sample size is the prerequisite of data analysis. It will help if the survey results can college more valid data.

@@

```{r university-education-vs-crime, fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message = FALSE}
cross_compare_barplot(data=gss_data %>% filter(msvic < 900) %>% filter(eor_01c < 3),
                            col1 = "eor_01c", col2 = "msvic",
                      col1_num=eor_01c_num, col1_labels=eor_01c_label,
                      col2_num=msvic_num, col2_labels=msvic_labels, 
                      plot_title="University Education VS Crime",
                      plot_subtitle="",
                      plot_xlab="Crime",
                      plot_ylab="Percentage", 
                      plot_fill_lab="Education")
```

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Lantao Cui
  - Huakun Shen
  - Sijian Wu
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

## Table of Contents
### 1  Introduction\
------------------------------------------------------------------------------------------------2

### 2  Data
##### 2.1 Data Source\
------------------------------------------------------------------------------------------------3

##### 2.2 Methodology and Data Collection\
------------------------------------------------------------------------------------------------3

##### 2.3 Data Characteristics\
------------------------------------------------------------------------------------------------5

### 3 Limitations and Conclusion\
------------------------------------------------------------------------------------------------9

### 4 Reference\
------------------------------------------------------------------------------------------------10
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)

@@

You can and should cross-reference sections and sub-sections. For instance, Section \@ref(data). R Markdown automatically makes the sections lower case and adds a dash to spaces to generate labels, for instance, Section \@ref(first-discussion-point).

@@

```{r, include= FALSE}
myvars <- c("sex", "cip_10")
cip_based_on_gender <- input_csv[myvars]
cip_based_on_gender<-cip_based_on_gender[!cip_based_on_gender$cip_10>=6,]
cip_based_on_gender$sex[cip_based_on_gender$sex==2] <- "Female"
cip_based_on_gender$sex[cip_based_on_gender$sex==1] <- "Male"
cip_based_on_gender$cip_10[cip_based_on_gender$cip_10==1] <- "Great confidence"
cip_based_on_gender$cip_10[cip_based_on_gender$cip_10==2] <- "Some confidence"
cip_based_on_gender$cip_10[cip_based_on_gender$cip_10==3] <- "Small confidence"
cip_based_on_gender$cip_10[cip_based_on_gender$cip_10==4] <- "No confidence"

cip_count_based_on_gender <- table(cip_based_on_gender$sex, cip_based_on_gender$cip_10)

@@

```{r, include = FALSE}
myvars <- c("sex", "plp_130", "plp_140")
pip_based_on_gender <- input_csv[myvars]
pip_based_on_gender<-pip_based_on_gender[!(pip_based_on_gender$plp_130>=6 | pip_based_on_gender$plp_140>=6),]
pip_based_on_gender$sex[pip_based_on_gender$sex==2] <- "Female"
pip_based_on_gender$sex[pip_based_on_gender$sex==1] <- "Male"
pip_based_on_gender$plp_130[pip_based_on_gender$plp_130==1] <- "Good Job"
pip_based_on_gender$plp_130[pip_based_on_gender$plp_130==2] <- "Average Job"
pip_based_on_gender$plp_130[pip_based_on_gender$plp_130==3] <- "Poor Job"

@@

```{r, include = FALSE}
myvars <- c("sex", "pcc_145")
conf_in_court_based_on_gender <- input_csv[myvars]
conf_in_court_based_on_gender<-conf_in_court_based_on_gender[!(conf_in_court_based_on_gender$pcc_145>=6),]
conf_in_court_based_on_gender$sex[conf_in_court_based_on_gender$sex==2] <- "Female"
conf_in_court_based_on_gender$sex[conf_in_court_based_on_gender$sex==1] <- "Male"
conf_in_court_based_on_gender$pcc_145[conf_in_court_based_on_gender$pcc_145==1] <- "Great Confidence"
conf_in_court_based_on_gender$pcc_145[conf_in_court_based_on_gender$pcc_145==2] <- "Some Confidence"
conf_in_court_based_on_gender$pcc_145[conf_in_court_based_on_gender$pcc_145==3] <- "Not Very Much Confidence"
conf_in_court_based_on_gender$pcc_145[conf_in_court_based_on_gender$pcc_145==4] <- "No Confidence"

conf_in_court_based_on_gender <- table(conf_in_court_based_on_gender$sex, conf_in_court_based_on_gender$pcc_145)

@@

@@

```{r fig.width=8, fig.height=5, echo=FALSE, warning=FALSE, message = FALSE}
cross_compare_barplot(data=gss_data %>% filter(msvic < 900) %>% filter(eduf10 < 6),
                            col1 = "edum5", col2 = "msvic",
                      col1_num=eduf10_num, col1_labels=eduf10_labels,
                      col2_num=msvic_num, col2_labels=msvic_labels, 
                      plot_title="Father Education VS Crime", 
                      plot_subtitle="Relatively low crime rate for all crimes", 
                      plot_xlab="Crime", 
                      plot_ylab="Percentage of Father Education", 
                      plot_fill_lab="Education")
```
